Supplement for: Carbon cycling in mature and regrowth forests globally: a macroecological synthesis based on the global Forest Carbon (ForC) database

### 2020-09-24 manuscript/ERL_global_C_review.Rmd
calculate stats
#29

#ForC raw
ForC_measurements <- read.csv("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/ForC/data/ForC_measurements.csv", stringsAsFactors = FALSE, check.names = FALSE)
ForC_plots <- read.csv("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/ForC/data/ForC_plots.csv", stringsAsFactors = FALSE, check.names = FALSE)
ForC_sites <- read.csv("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/ForC/data/ForC_sites.csv", stringsAsFactors = FALSE, check.names = FALSE)
n_areas <- max(ForC_sites[,"geographic.area"], na.rm = TRUE )

@@

#stats I haven't yet acquired:
n_records_age_unk <- NA  #total n records no age info
n_records_coord_unk <- NA  #total n records no geographic coordinates

@@

@@

For this analysis, we grouped forests into four broad biome types (tropical broadleaf, temperate broadleaf, temperate needleleaf, and boreal needleleaf) and two age classifications (young and mature). 
Climate zones (Fig. 1) were defined based on site geographic coordinates according to Köppen-Geiger zones (Rubel and Kottek 2010).
Tropical climates were defined to include all equatorial (A) zones, temperate climates were defined to include all warm temperate (C) zones and warmer snow climates (Dsa, Dsb, Dwa, Dwb, Dfa, and Dfb), and boreal climates were defined to include the colder snow climates (Dsc, Dsd, Dwc, Dwd, Dfc, and Dfd). 
Any forests in dry (B) and polar (E) Köppen-Geiger zones were excluded from the analysis. 
Leaf type (broadleaf / needleleaf) was defined based on descriptions in original publications (prioritized) or values extracted from a global map based on satellite observations [SYNMAP; @jung_exploiting_2006]. 
Forests were classified as “young” (< 100 years) or “mature” ($\ge$ 100 years or classified as “mature”, “old growth”, “intact”, or “undisturbed” in original publication). 
Assigning stands to these groupings required the exclusion of records for which ForC lacked records of stand age (n=`r round(n_records_age_unk/nrow(ForC_measurements)*100, digits=1)`% of total database), or geographic coordinates (n=`r round(n_records_coord_unk/nrow(ForC_measurements)*100, digits=1)`% of total database). 
In total, our analysis retained `r round(n_records/n_focal_variable_records_eligible_for_inclusion*100, digits=1)` of the focal variable records for forests of known age. 
The most well-represented forest types excluded were boreal broadleaf (`r n_records_BoB` records) and boreal and temperate mixed broadleaf-needleleaf (`r n_records_Bomixed` and `r n_records_Te_mixed` records, respectively).

>>>>

#ForC raw
ForC_measurements <- read.csv("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/ForC/data/ForC_measurements.csv", stringsAsFactors = FALSE, check.names = FALSE)
  n_records_age_unk <- sum(is.na(as.numeric(ForC_measurements[, "stand.age"])))  #total n records no age info
ForC_plots <- read.csv("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/ForC/data/ForC_plots.csv", stringsAsFactors = FALSE, check.names = FALSE)
ForC_sites <- read.csv("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/ForC/data/ForC_sites.csv", stringsAsFactors = FALSE, check.names = FALSE)
  n_sites_coord_unk <- sum(is.na(as.numeric(ForC_sites[, "lat"])))  #total n records no geographic coordinates
  n_areas <- max(ForC_sites[,"geographic.area"], na.rm = TRUE )

@@

@@

*(Abby has offered to update stats in this paragraph:)*

@@

For this analysis, we grouped forests into four broad biome types (tropical broadleaf, temperate broadleaf, temperate needleleaf, and boreal needleleaf) and two age classifications (young and mature). 
Climate zones (Fig. 1) were defined based on site geographic coordinates according to Köppen-Geiger zones (Rubel and Kottek 2010).
Tropical climates were defined to include all equatorial (A) zones, temperate climates were defined to include all warm temperate (C) zones and warmer snow climates (Dsa, Dsb, Dwa, Dwb, Dfa, and Dfb), and boreal climates were defined to include the colder snow climates (Dsc, Dsd, Dwc, Dwd, Dfc, and Dfd). 
Any forests in dry (B) and polar (E) Köppen-Geiger zones were excluded from the analysis. 
Leaf type (broadleaf / needleleaf) was defined based on descriptions in original publications (prioritized) or values extracted from a global map based on satellite observations [SYNMAP; @jung_exploiting_2006]. 
Forests were classified as “young” (< 100 years) or “mature” ($\ge$ 100 years or classified as “mature”, “old growth”, “intact”, or “undisturbed” in original publication). 
Assigning stands to these groupings required the exclusion of records for which ForC lacked records of stand age (n=`r round(n_records_age_unk/nrow(ForC_measurements)*100, digits=1)`% of records in full database), or geographic coordinates (n=`r round(n_sites_coord_unk/nrow(ForC_sites)*100, digits=1)`% of sites in full database). 
In total, our analysis retained `r round(n_records/n_focal_variable_records_eligible_for_inclusion*100, digits=1)` of the focal variable records for forests of known age. 
The most well-represented forest types excluded were boreal broadleaf (`r n_records_BoB` records) and boreal and temperate mixed broadleaf-needleleaf (`r n_records_Bomixed` and `r n_records_Te_mixed` records, respectively).
